\headright{Experience}

\jobtitle{DevOps Engineer}{Alten (France)}{2025.05 -- 2026.03}{}
\small

\noindent \textbf{Amadeus}

\begin{itemize}[label=\tiny$\bullet$, leftmargin=1em]
	\item Migrated legacy Groovy pipeline scripts to an internal framework handling full app lifecycles.
	\item Rewrote feed framework from \textbf{Bash} to \textbf{Python} for scheduled data deliveries.
	\item Introduced industry frameworks to automate local dependencies (Localstack, Nix devenv).
	\item Developed scripts to dynamically switch machine types on EMR clusters from spot to on-demand based on queue latency.
	\item Overhauled internal documentation for improved clarity and maintainability.
	\item Designed an HLD for release management, standardizing deployment workflows in accordance with change management requirements.
\end{itemize}

\vspace{3.0ex}
\jobtitle{DevOps Engineer}{DXC Technology (Bulgaria)}{2022.02 -- 2025.04}{}
\small

\noindent \textbf{Continental AG (Tires)}
\begin{itemize}[label=\tiny$\bullet$, leftmargin=1em, nosep]
	\item Led a 5-person team and directly reported project status to the client.
	\item Optimized data processing logic by migrating legacy Spark batch jobs to Apache Flink streaming pipelines, significantly reducing latency.
	\item Accelerated project kickoff by resolving critical VPN connectivity issues and automating local development procedures.
\end{itemize}

\vspace{1em}
\noindent \textbf{Nestle}
\begin{itemize}[label=\tiny$\bullet$, leftmargin=1em, nosep]
	\item Implemented automated structural validation checks for Pull Requests to prevent non-compliant deployments.
	\item Extended Snowflake dialects in SQLFluff and automated integration in the pre-release step
	\item Integrated ANTLR parsers into the \textbf{CI/CD} pipeline as a mandatory pre-release validation gate.
\end{itemize}

\vspace{1em}
\noindent \textbf{Ahold Delhaize}
\begin{itemize}[label=\tiny$\bullet$, leftmargin=1em]
	\item Redesigned the Test Automation Framework into a modular architecture, improving code reusability and reducing onboarding time for QA engineers.
	\item Collaborated with the QA team in weekly syncs to identify operational bottlenecks, resulting in improved team autonomy.
	\item Designed an HLD for cross-environment data sharing, that supported the migration of the new cloud ingestion framework (CF2).
	\item Automated a flow to host Allure reports as static website on Azure Blob Storage with custom authentication middleware.
	\item Led a technical evaluation of \textbf{SonarQube} for automated code analysis, in order to identify integration requirements for the platform
\end{itemize}

\vspace{1em}
\noindent \textbf{Continental AG (ADAS, codename CAEdge)}
\begin{itemize}[label=\tiny$\bullet$, leftmargin=1em]
	\item Automated a standardized \textbf{VPC} topology for a multi-account AWS setup, integrating it into the Account Vending Machine orchestrator.
	\item Designed and automated a cloud-cost governance solution across a multi-account AWS organization, implementing budget alerts to prevent overruns.
	\item Reduced the attack surface of cloud applications by remediating CVEs identified by AWS Inspector reports.
\end{itemize}

\vspace{5.0ex}
\jobtitle{Software Engineer Intern}{Sys Consulting Ltd.}{2021.07 -- 2021.12}{}
\small
Maintained legacy banking systems in CAVO for Windows XP environments.
